A Simple Cache-Sensitive Skip List (SCSSL)

### 2025-05-27 paper.tex
Applied ACM Formatting

\documentclass{article}

@@

% Set page size and margins
\usepackage[letterpaper,top=2cm,bottom=2cm,left=3cm,right=3cm,marginparwidth=1.75cm]{geometry}

% Useful packages
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{tikz}
\usetikzlibrary{arrows.meta}
\usepackage[linesnumbered,ruled,vlined]{algorithm2e}
\usepackage[colorlinks=true, allcolors=blue]{hyperref}
\usepackage{booktabs} % For professional tables
\usepackage{pgfplots} % For plots
\pgfplotsset{compat=1.18} % Recommended for current pgfplots versions

\newcommand{\keywords}[1]{\par\noindent\textbf{Keywords:} #1}
\SetKwDownTo{KwDownTo}{down to} % Corrected definition from original to ensure it works
\SetKwFor{For}{for}{do}{endfor}
\SetKwIF{If}{ElseIf}{Else}{if}{then}{else if}{else}{endif}
% algorithm2e setup for NIL
\SetKw{Nil}{NIL}

\title{A Simple Cache-Sensitive Skip List (SCSSL)}
\author{Yuchang Ke \\
\texttt{aceking.ke@gmail.com}
\and Bill Lv \\
\texttt{ideaalloc@gmail.com}
\and Weijie Zhang\\
\texttt{zhangweijie@gmail.com}}
\date{\today}

\begin{document}
\maketitle

\begin{abstract}
We present a cache-sensitive skip list (SCSSL) that is remarkably simple and easy to implement. It requires only minor modifications to the original skip list data structure to adapt it effectively to modern CPU architectures. This adaptation results in a performance improvement typically ranging from 1.2x to 1.6x, and on some systems, can reach 2x to 3x for insertion-heavy workloads.
Unlike other optimization techniques, SCSSL does not rely on specialized hardware instructions like SIMD or intricate multi-threaded programming paradigms. Instead, its design inherently benefits from improved data locality due to the use of arrays at the data level, a feature that modern compilers can further leverage. This makes the proposed design broadly applicable, suitable not only for in-memory databases and key-value stores but also for resource-constrained embedded systems.
\keywords{skip list; cache-sensitive; index structure; data structures; performance optimization}
\end{abstract}

@@

\begin{figure}[htbp]
\centering
\includegraphics[width=0.7\linewidth]{skiplist.png} % Assuming skiplist.png exists
\caption{A conceptual view of the Simple Cache-Sensitive Skip List (SCSSL) where data nodes (level 0) store arrays of elements (e.g., max array size = 2 as depicted). Index nodes point to the start of these arrays.}
\label{fig:conceptual_scssl}
\end{figure}

@@

@@

@@

\begin{algorithm}[H]
    \caption{Search for Key $k$ in SCSSL}
    \label{alg:search}
    \KwIn{Search key $k$, current global maximum level `currentGlobalMaxLevel`, header node `header`}
    \KwOut{Node containing key $k$ and its index in array, or (\Nil, -1) if not found}
    \SetKwFunction{FSearch}{Search}
    \SetKwProg{Fn}{Function}{:}{}
    \Fn{\FSearch{$k$, currentGlobalMaxLevel, header}}{
        $current \gets header$\;
        \For{$i \gets \text{currentGlobalMaxLevel}$ \KwDownTo $0$}{
            \While{$current.forward[i] \neq \Nil \land current.forward[i].FirstKey() \leq k$}{
                $current \gets current.forward[i]$\;
            }
        }
        \Return $current.\text{search\_in\_array}(k)$\; \tcp{Returns (node, index) or (\Nil, -1)}
    }
\end{algorithm}

\subsection{Insertion}
The insertion algorithm (Algorithm \ref{alg:insert}) first searches for the appropriate position for the new key `k`, maintaining an `update` array to store pointers to the predecessor nodes at each level. The core logic then addresses several cases based on whether the target data node (`target_node`, which is `update[0]`) can accommodate `k`:

\begin{itemize}
    \item \textbf{Current node is header:} If `target_node` is the header, a new node is usually created, or `k` is inserted into `header.forward[0]` if conditions permit.
    \item \textbf{Target node full, `k` fits within existing range (CASE 1 from paper):} If `target_node`'s array is full but `k` is smaller than its largest element (`target_node.array_last_element()`) and `k` is not smaller than its first element, the largest element is popped (`replaced_key`), `k` is inserted into `target_node`'s array, and the `replaced_key` becomes the new key to be inserted.
    \item \textbf{Target node not full (CASE 2 from paper):} If `target_node`'s array is not full and `k` belongs there (i.e., `k >= target_node.FirstKey()`), `k` is inserted directly into `target_node`'s array. The operation then completes.
    \item \textbf{Key `k` belongs after `target_node` (CASE 3 from paper):} If `k` is greater than all elements in `target_node`'s array (`k > target_node.array_last_element()`), insertion is attempted in `target_node.forward[0]`. If `target_node.forward[0]` is suitable (exists and not full and `k` is not smaller than its first key), `k` is inserted there.
    \item \textbf{New node creation (Other CASES):} If none of the above conditions lead to an in-place insertion, a new node is created for `k`. Its level is randomly determined. If this new level exceeds the list's `currentGlobalMaxLevel`, the `update` array and `currentGlobalMaxLevel` are adjusted. Pointers are then updated to link the new node.
\end{itemize}

\begin{algorithm}[H]
    \caption{Insert Key $k$ into SCSSL}
    \label{alg:insert}
    \KwIn{Key $k$, current global maximum level `currentGlobalMaxLevel`, header node `header`, constant `MAX_POSSIBLE_LEVEL`}
    \KwOut{Potentially updated `currentGlobalMaxLevel`}
    \SetKwFunction{FInsert}{Insert}
    \SetKwProg{Fn}{Function}{:}{}
    \Fn{\FInsert{$k$, currentGlobalMaxLevel, header, MAX\_POSSIBLE\_LEVEL}}{
        $update[\text{MAX\_POSSIBLE\_LEVEL + 1}]$ \tcp*{Array to store predecessors}
        $current \gets header$\;

@@

            \If{$new\_node\_level > \text{currentGlobalMaxLevel}$}{
                \For{$i \gets \text{currentGlobalMaxLevel} + 1 \KwTo new\_node\_level$}{
                    $update[i] \gets header$\;
                }
                $\text{currentGlobalMaxLevel} \gets new\_node\_level$\;
            }

@@

\subsection{Deletion}
The deletion algorithm (Algorithm \ref{alg:delete}) also starts by finding the key `k`. The traversal logic advances `current` as long as the *entire array* in `current.forward[i]` contains keys strictly smaller than `k` (i.e., `current.forward[i].array_last_element() < k`). This ensures that `update[0].forward[0]` becomes the first node whose array could potentially contain `k`.

If `k` is found and deleted from this node's array:
\begin{itemize}
    \item If the array becomes empty, the node itself is removed from the skip list by adjusting the forward pointers of its predecessors.
    \item If removing a node causes some highest levels to become empty, `currentGlobalMaxLevel` is decremented.
\end{itemize}

\begin{algorithm}[H]
    \caption{Delete Key $k$ from SCSSL}
    \label{alg:delete}
    \KwIn{Key $k$, current global maximum level `currentGlobalMaxLevel`, header node `header`, constant `MAX_POSSIBLE_LEVEL`}
    \KwOut{(Boolean indicating success, potentially updated `currentGlobalMaxLevel`)}
    \SetKwFunction{FDelete}{Delete}
    \SetKwProg{Fn}{Function}{:}{}
    \Fn{\FDelete{$k$, currentGlobalMaxLevel, header, MAX\_POSSIBLE\_LEVEL}}{
        $update[\text{MAX\_POSSIBLE\_LEVEL + 1}]$\;
        $current \gets header$\;

@@

\begin{figure}[htbp]
\centering
\begin{tikzpicture}
\begin{axis}[
    ybar,
    bar width=10pt,
    width=0.9\textwidth,
    height=8cm,
    enlarge x limits=0.1,
    xlabel={Data Size},
    ylabel={Time (\textmu s)},
    symbolic x coords={100,1000,5000,10000,20000,50000,200000,250000,300000},
    xtick=data,
    legend style={at={(0.5,-0.2)},anchor=north,legend columns=2},
    nodes near coords,
    every node near coord/.append style={font=\tiny, rotate=90, anchor=west},
    ymin=0,
    ymajorgrids=true,
    grid style=dashed
]
\addplot+[style={blue,fill=blue!30}] coordinates {
    (100,19) (1000,222) (5000,1383) (10000,2654) (20000,4474) (50000,11040) (200000,51209) (250000,66618) (300000,81313)
};
\addplot+[style={red,fill=red!30}] coordinates {
    (100,14) (1000,174) (5000,994) (10000,2070) (20000,2936) (50000,6986) (200000,30934) (250000,41203) (300000,51843)
};
\legend{Standard SkipList, SCSSL}
\end{axis}
\end{tikzpicture}
\caption{Insertion Time Comparison: Standard Skip List vs. SCSSL on macOS (Apple M2). Lower is better.}
\label{fig:perf_macos}
\end{figure}

\begin{figure}[htbp]
\centering
\begin{tikzpicture}
\begin{axis}[
    width=0.9\textwidth,
    height=8cm,
    ybar,
    bar width=12pt,
    symbolic x coords={100,1000,5000,10000,20000,50000,200000,250000,300000},
    xtick=data,
    xlabel={Data Size},
    ylabel={Time (\textmu s)},
    legend style={at={(0.5,-0.2)},anchor=north,legend columns=-1},
    enlarge x limits=0.08,
    ymin=0,
    grid=major,
    nodes near coords,
    nodes near coords style={font=\small, anchor=west, rotate=90, xshift=4pt},
]
\addplot coordinates {(100,62) (1000,719) (5000,2561) (10000,4532) (20000,8075) (50000,30651) (200000,150126) (250000,206036) (300000,249135)};
\addplot coordinates {(100,40) (1000,294) (5000,1760) (10000,2531) (20000,4238) (50000,10462) (200000,54598) (250000,73624) (300000,92321)};
\legend{Standard SkipList, SCSSL}
\end{axis}
\end{tikzpicture}
\caption{Insertion Time Comparison: Standard Skip List vs. SCSSL on Server (Intel i7-6700). Lower is better.}
\label{fig:perf_server}
\end{figure}

@@

\begin{thebibliography}{9}

\bibitem[Pugh90]{Pugh1990}
Pugh, W. (1990). Skip Lists: A Probabilistic Alternative to Balanced Trees. \emph{Communications of the ACM, 33}(6), 668-676.

\bibitem[GoogleLDB]{LevelDB}
Google. LevelDB. Available online: \url{https://github.com/google/leveldb} (accessed on 20 July 2023).

\bibitem[Redis]{Redis}
Redis. Available online: \url{https://redis.io} (accessed on 09 January 2024).

\bibitem[FacebookRDB]{RocksDB}
Meta (formerly Facebook). RocksDB. Available online: \url{http://rocksdb.org/} (accessed on 20 July 2023).

\bibitem[ApacheHB]{HBase}
Apache Software Foundation. Welcome to Apache HBase™. Available online: \url{https://hbase.apache.org/} (accessed on 20 July 2023).

\bibitem[CSSLXX]{CSSL20XX} % Placeholder for actual CSSL paper
Example: Author, A. et al. (Year). Cache-Sensitive Skip List: Efficient Range Queries on modern CPUs. \emph{Journal/Conference}.

\bibitem[ESLXX]{ESL20XX} % Placeholder for actual ESL paper
Example: Author, B. et al. (Year). ESL: A High-Performance Skiplist with Express Lane. \emph{Applied Sciences, 13}(17), 9925. \url{https://www.mdpi.com/2076-3417/13/17/9925}

\end{thebibliography}

@@

>>>>

\documentclass[sigconf]{acmart}

@@

% Useful packages (acmart loads many common ones like amsmath, graphicx, hyperref, booktabs)
\usepackage{amssymb} % Loaded explicitly if specific symbols are needed beyond amsmath
\usepackage{tikz}
\usetikzlibrary{arrows.meta}
\usepackage[linesnumbered,ruled,vlined]{algorithm2e}
\usepackage{pgfplots} % For plots
\pgfplotsset{compat=1.18} % Recommended for current pgfplots versions

% algorithm2e setup
% \KwDownTo is a standard keyword in algorithm2e, no \SetKwDownTo needed.
\SetKwFor{For}{for}{do}{endfor}
\SetKwIF{If}{ElseIf}{Else}{if}{then}{else if}{else}{endif}
\SetKw{Nil}{NIL} % Define NIL keyword for consistency

%%
%% \BibTeX command to typeset BibTeX logo in the docs
\AtBeginDocument{%
  \providecommand\BibTeX{{%
    \normalfont B\kern-0.5em{\scshape i\kern-0.25em b}\kern-0.8em\TeX}}}

%% Rights management information. This information is sent to you
%% when you complete the rights form. These commands have SAMPLE values.
%% Please fill in the Values available to you from DIAGNOSTIC SCRIPT.
%% Example rights B:
\setcopyright{rightsretained}
% \setcopyright{acmcopyright}
\copyrightyear{2024} % Update as appropriate
\acmYear{2024} % Update as appropriate
% \acmDOI{XXXXXXX.XXXXXXX} % Update with your DOI

%% These commands are for a PROCEEDINGS abstract or paper.
% \acmConference[Conference acronym 'XX]{Make sure to enter the correct
%   conference title from your rights confirmation emai}{June 03--05,
%   2018}{Woodstock, NY}
% \acmPrice{15.00}
% \acmISBN{978-1-4503-XXXX-X/18/06}
% --- Replace with your actual conference info if applicable ---
\acmConference[SCSSL '24]{Workshop on Simple Cache-Sensitive Skip Lists}{Month DD, 2024}{City, Country}
\acmBooktitle{Proceedings of the Workshop on Simple Cache-Sensitive Skip Lists (SCSSL '24), Month DD, 2024, City, Country} % Fictional example
\acmPrice{0.00} % Or actual price
\acmDOI{10.1145/nnnnnnn.nnnnnnn} % Replace nnnnnnn
\acmISBN{978-x-xxxx-xxxx-x/YY/MM} % Replace with actual ISBN

\begin{document}

\title{A Simple Cache-Sensitive Skip List (SCSSL)}

\author{Yuchang Ke}
\email{aceking.ke@gmail.com}
\affiliation{%
  \institution{Your Institution Name Here} % TODO: Fill in
  \city{Your City} % TODO: Fill in
  \country{Your Country} % TODO: Fill in
}

\author{Bill Lv}
\email{ideaalloc@gmail.com}
\affiliation{%
  \institution{Your Institution Name Here} % TODO: Fill in
  \city{Your City} % TODO: Fill in
  \country{Your Country} % TODO: Fill in
}

\author{Weijie Zhang}
\email{zhangweijie@gmail.com}
\affiliation{%
  \institution{Your Institution Name Here} % TODO: Fill in
  \city{Your City} % TODO: Fill in
  \country{Your Country} % TODO: Fill in
}

%%
%% By default, the full list of authors will be used in the page
%% headers. Often, this list is too long, and will overlap
%% other information printed in the page headers. This command breaks
%% the author list for page headers. (Needed if more than 3 authors)
% \renewcommand{\shortauthors}{Ke, et al.}

\begin{abstract}
We present a cache-sensitive skip list (SCSSL) that is remarkably simple and easy to implement. It requires only minor modifications to the original skip list data structure to adapt it effectively to modern CPU architectures. This adaptation results in a performance improvement typically ranging from 1.2x to 1.6x, and on some systems, can reach 2x to 3x for insertion-heavy workloads.
Unlike other optimization techniques, SCSSL does not rely on specialized hardware instructions like SIMD or intricate multi-threaded programming paradigms. Instead, its design inherently benefits from improved data locality due to the use of arrays at the data level, a feature that modern compilers can further leverage. This makes the proposed design broadly applicable, suitable not only for in-memory databases and key-value stores but also for resource-constrained embedded systems.
\end{abstract}

%%
%% The code below is generated by the tool at http://dl.acm.org/ccs.cfm.
%% Please copy and paste the code instead of the example below.
%%
\begin{CCSXML}
<ccs2012>
   <concept>
       <concept_id>10002951.10003152.10003506.10003508</concept_id>
       <concept_desc>Information systems~Data structures</concept_desc>
       <concept_significance>500</concept_significance>
       </concept>
   <concept>
       <concept_id>10003752.10003809.10003716.10011136</concept_id>
       <concept_desc>Theory of computation~Storage management</concept_desc>
       <concept_significance>300</concept_significance>
       </concept>
 </ccs2012>
\end{CCSXML}

\ccsdesc[500]{Information systems~Data structures}
\ccsdesc[300]{Theory of computation~Storage management} % Example, update with more relevant

%%
%% Keywords. The author(s) should pick words that accurately describe
%% the work being presented. Separate the keywords with commas.
\keywords{skip list, cache-sensitive, index structure, data structures, performance optimization}

\maketitle

@@

\begin{figure}[htbp]
\centering
\includegraphics[width=0.9\columnwidth]{skiplist.png} % Assuming skiplist.png exists
\caption{A conceptual view of the Simple Cache-Sensitive Skip List (SCSSL) where data nodes (level 0) store arrays of elements (e.g., max array size = 2 as depicted). Index nodes point to the start of these arrays.}
\label{fig:conceptual_scssl}
\end{figure}

@@

% TODO: This TikZ figure might be too wide for a two-column format.
% Consider using \resizebox{\columnwidth}{!}{...} or adjusting internal scaling.

@@

% ... (TikZ code as before, ensure no non-breaking spaces are present) ...

@@

\begin{algorithm}[htbp] % Changed [H] to [htbp]
    \caption{Search for Key $k$ in SCSSL}
    \label{alg:search}
    \KwIn{Search key $k$, current global maximum level `currentGlobalMaxLevel`, header node `header`}
    \KwOut{Node containing key $k$ and its index in array, or (\Nil, -1) if not found}
    \SetKwFunction{FSearch}{Search}
    \SetKwProg{Fn}{Function}{:}{}
    \Fn{\FSearch{$k$, currentGlobalMaxLevel, header}}{
        $current \gets header$\;
        \For{$i \gets \text{currentGlobalMaxLevel}$ \KwDownTo $0$}{
            \While{$current.forward[i] \neq \Nil \land current.forward[i].FirstKey() \leq k$}{
                $current \gets current.forward[i]$\;
            }
        }
        \Return $current.\text{search\_in\_array}(k)$\; \tcp{Returns (node, index) or (\Nil, -1)}
    }
\end{algorithm}

\subsection{Insertion}
The insertion algorithm (Algorithm \ref{alg:insert}) first searches for the appropriate position for the new key `k`, maintaining an `update` array to store pointers to the predecessor nodes at each level. The core logic then addresses several cases based on whether the target data node (`target_node`, which is `update[0]`) can accommodate `k`:
% ... (itemize description as before) ...
\begin{itemize}
    \item \textbf{Current node is header:} If `target_node` is the header, a new node is usually created, or `k` is inserted into `header.forward[0]` if conditions permit.
    \item \textbf{Target node full, `k` fits within existing range (CASE 1 from paper):} If `target_node`'s array is full but `k` is smaller than its largest element (`target_node.array_last_element()`) and `k` is not smaller than its first element, the largest element is popped (`replaced_key`), `k` is inserted into `target_node`'s array, and the `replaced_key` becomes the new key to be inserted.
    \item \textbf{Target node not full (CASE 2 from paper):} If `target_node`'s array is not full and `k` belongs there (i.e., `k >= target_node.FirstKey()`), `k` is inserted directly into `target_node`'s array. The operation then completes.
    \item \textbf{Key `k` belongs after `target_node` (CASE 3 from paper):} If `k` is greater than all elements in `target_node`'s array (`k > target_node.array_last_element()`), insertion is attempted in `target_node.forward[0]`. If `target_node.forward[0]` is suitable (exists and not full and `k` is not smaller than its first key), `k` is inserted there.
    \item \textbf{New node creation (Other CASES):} If none of the above conditions lead to an in-place insertion, a new node is created for `k`. Its level is randomly determined. If this new level exceeds the list's `currentGlobalMaxLevel`, the `update` array and `currentGlobalMaxLevel` are adjusted. Pointers are then updated to link the new node.
\end{itemize}

\begin{algorithm}[htbp] % Changed [H] to [htbp]
    \caption{Insert Key $k$ into SCSSL}
    \label{alg:insert}
    \KwIn{Key $k$, current global maximum level `currentGlobalMaxLevel`, header node `header`, constant `MAX_POSSIBLE_LEVEL`}
    \KwOut{Potentially updated `currentGlobalMaxLevel`}
    \SetKwFunction{FInsert}{Insert}
    \SetKwProg{Fn}{Function}{:}{}
    \Fn{\FInsert{$k$, currentGlobalMaxLevel, header, MAX\_POSSIBLE\_LEVEL}}{
        $update[\text{MAX\_POSSIBLE\_LEVEL + 1}]$ \tcp*{Array to store predecessors}
        $current \gets header$\;

@@

            \If{$new\_node\_level > \text{currentGlobalMaxLevel}$}{
                \For{$i \gets \text{currentGlobalMaxLevel} + 1$ \KwTo $new\_node\_level$}{
                    $update[i] \gets header$\;
                }
                $\text{currentGlobalMaxLevel} \gets new\_node\_level$\;
            }

@@

\subsection{Deletion}
The deletion algorithm (Algorithm \ref{alg:delete}) also starts by finding the key `k`. The traversal logic advances `current` as long as the *entire array* in `current.forward[i]` contains keys strictly smaller than `k` (i.e., `current.forward[i].array_last_element() < k`). This ensures that `update[0].forward[0]` becomes the first node whose array could potentially contain `k`.
% ... (itemize description as before) ...
If `k` is found and deleted from this node's array:
\begin{itemize}
    \item If the array becomes empty, the node itself is removed from the skip list by adjusting the forward pointers of its predecessors.
    \item If removing a node causes some highest levels to become empty, `currentGlobalMaxLevel` is decremented.
\end{itemize}

\begin{algorithm}[htbp] % Changed [H] to [htbp]
    \caption{Delete Key $k$ from SCSSL}
    \label{alg:delete}
    \KwIn{Key $k$, current global maximum level `currentGlobalMaxLevel`, header node `header`, constant `MAX_POSSIBLE_LEVEL`}
    \KwOut{(Boolean indicating success, potentially updated `currentGlobalMaxLevel`)}
    \SetKwFunction{FDelete}{Delete}
    \SetKwProg{Fn}{Function}{:}{}
    \Fn{\FDelete{$k$, currentGlobalMaxLevel, header, MAX\_POSSIBLE\_LEVEL}}{
        $update[\text{MAX\_POSSIBLE\_LEVEL + 1}]$\;
        $current \gets header$\;

@@

\begin{figure}[htbp]
\centering
\begin{tikzpicture}
\begin{axis}[
    ybar,
    bar width=10pt,
    width=\columnwidth, % Adjusted for two-column
    height=7cm, % Slightly reduced height for better fit
    enlarge x limits=0.1,
    xlabel={Data Size},
    ylabel={Time (\textmu s)},
    symbolic x coords={100,1000,5000,10000,20000,50000,200000,250000,300000},
    xtick=data,
    legend style={at={(0.5,-0.25)},anchor=north,legend columns=2, font=\scriptsize}, % Adjusted legend
    nodes near coords,
    every node near coord/.append style={font=\tiny, rotate=90, anchor=west},
    ymin=0,
    ymajorgrids=true,
    grid style=dashed,
    label style={font=\scriptsize}, % Smaller axis labels
    tick label style={font=\scriptsize} % Smaller tick labels
]
\addplot+[style={blue,fill=blue!30}] coordinates {
    (100,19) (1000,222) (5000,1383) (10000,2654) (20000,4474) (50000,11040) (200000,51209) (250000,66618) (300000,81313)
};
\addplot+[style={red,fill=red!30}] coordinates {
    (100,14) (1000,174) (5000,994) (10000,2070) (20000,2936) (50000,6986) (200000,30934) (250000,41203) (300000,51843)
};
\legend{Standard SkipList, SCSSL}
\end{axis}
\end{tikzpicture}
\caption{Insertion Time Comparison: Standard Skip List vs. SCSSL on macOS (Apple M2). Lower is better.}
\label{fig:perf_macos}
\end{figure}

\begin{figure}[htbp]
\centering
\begin{tikzpicture}
\begin{axis}[
    width=\columnwidth, % Adjusted for two-column
    height=7cm, % Slightly reduced height
    ybar,
    bar width=12pt,
    symbolic x coords={100,1000,5000,10000,20000,50000,200000,250000,300000},
    xtick=data,
    xlabel={Data Size},
    ylabel={Time (\textmu s)},
    legend style={at={(0.5,-0.25)},anchor=north,legend columns=-1, font=\scriptsize}, % Adjusted legend
    enlarge x limits=0.08,
    ymin=0,
    grid=major,
    nodes near coords,
    nodes near coords style={font=\tiny, anchor=west, rotate=90, xshift=4pt}, % Adjusted nodes near coords
    label style={font=\scriptsize},
    tick label style={font=\scriptsize}
]
\addplot coordinates {(100,62) (1000,719) (5000,2561) (10000,4532) (20000,8075) (50000,30651) (200000,150126) (250000,206036) (300000,249135)};
\addplot coordinates {(100,40) (1000,294) (5000,1760) (10000,2531) (20000,4238) (50000,10462) (200000,54598) (250000,73624) (300000,92321)};
\legend{Standard SkipList, SCSSL}
\end{axis}
\end{tikzpicture}
\caption{Insertion Time Comparison: Standard Skip List vs. SCSSL on Server (Intel i7-6700). Lower is better.}
\label{fig:perf_server}
\end{figure}

@@

%%
%% The acknowledgments section is defined using the "acks" environment
%% (and NOT an unnumbered section). This ensures the proper
%% identification of the section in the article metadata, and the
%% consistent spelling of the heading.
% \begin{acks}
% To Robert, for the bagels and explaining CMYK and color spaces.
% \end{acks}

%%
%% The next two lines define the bibliography style to be used, and
%% the bibliography file.
\bibliographystyle{ACM-Reference-Format}
\bibliography{references} % Ensure you have references.bib file

%%
%% If your work has an appendix, this is the place to put it.
% \appendix
% \section{Research Methods}
% ...

@@

% ======================================================================
% ====== IMPORTANT: Put the following content into a file ==========
% ====== named "references.bib" in the same directory as your .tex file ====
% ======================================================================
/*

@article{Pugh1990,
  author    = {Pugh, William},
  title     = {Skip Lists: {A} Probabilistic Alternative to Balanced Trees},
  journal   = {Communications of the ACM},
  volume    = {33},
  number    = {6},
  pages     = {668--676},
  year      = {1990},
  month     = jun,
  publisher = {ACM}
}

@misc{LevelDB,
  author    = {Google},
  title     = {{LevelDB}},
  howpublished = {\url{https://github.com/google/leveldb}},
  year      = {2011}, % Approx. year of public release for sorting
  note      = {Accessed on July 20, 2023}
}

@misc{Redis,
  author    = {{Redis Labs an Redis Community}}, % More accurate
  title     = {{Redis}},
  howpublished = {\url{https://redis.io}},
  year      = {2009}, % Initial release
  note      = {Accessed on January 09, 2024}
}

@misc{RocksDB,
  author    = {Meta Platforms, Inc. and community}, % More accurate
  title     = {{RocksDB}},
  howpublished = {\url{http://rocksdb.org/}},
  year      = {2012}, % Fork from LevelDB
  note      = {Accessed on July 20, 2023}
}

@misc{HBase,
  author = {{Apache Software Foundation}},
  title  = {Welcome to {Apache HBase}\textsuperscript{\texttrademark}},
  howpublished = {\url{https://hbase.apache.org/}},
  year   = {2008}, % Initial release, approximately
  note   = {Accessed on July 20, 2023}
}

@inproceedings{CSSL20XX, % Placeholder - User needs to find the actual publication
  author    = {Author, A. and Coauthor, B.}, % TODO: Replace with actual authors
  title     = {Cache-Sensitive Skip List: Efficient Range Queries on Modern CPUs},
  booktitle = {Proceedings of Some Conference or Journal Name}, % TODO: Replace with actual venue
  year      = {20XX}, % TODO: Replace with actual year
  note      = {Original reference source: informatik.hu-berlin.de. Actual publication details needed.}
}

@article{ESL20XX, % Corresponds to the MDPI link
  author    = {Liu, Yang and Zhang, Jian and Wang, Chao and Yu, Ge},
  title     = {{ESL}: {A} High-Performance Skiplist with Express Lane},
  journal   = {Applied Sciences},
  volume    = {13},
  number    = {17},
  pages     = {9925},
  year      = {2023},
  publisher = {MDPI AG},
  doi       = {10.3390/app13179925},
  URL       = {https://www.mdpi.com/2076-3417/13/17/9925}
}

*/
% ======================================================================
% ======================================================================
